\documentclass[SE,lsstdraft,authoryear,toc]{lsstdoc}
\input{meta}

% Package imports go here.

% Local commands go here.
\newcommand{\VeraRubinObservatory}{NSF-DOE Vera~C.~Rubin Observatory\xspace}

\newcommand{\figRef}[1]{Fig.~\ref{fig:#1}\xspace}
\newcommand{\figRefII}[2]{Figs.~\ref{fig:#1} and \ref{fig:#2}\xspace}
\newcommand{\figRefIII}[3]{Figs.~\ref{fig:#1}, \ref{fig:#2}, and \ref{fig:#3}\xspace}
\renewcommand{\secRef}[1]{Sec.~\ref{sec:#1}\xspace}
\newcommand{\tabRef}[1]{Tab.~\ref{tab:#1}\xspace}

%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{An Interim Report on the On-Sky Commissioning Campaign with LSSTCam}

% This can write metadata into the PDF.
% Update keywords and author information as necessary.
\hypersetup{
    pdftitle={An Interim Report on the On-Sky Commissioning Campaign with LSSTCam},
    pdfauthor={NSF-DOE Vera C. Rubin Observatory},
    pdfkeywords={}
}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\input{authors}

\setDocRef{SITCOMTN-170}
\setDocUpstreamLocation{\url{https://github.com/lsst-sitcom/sitcomtn-170}}

\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
From 15 April to 21 September 2025, the \VeraRubinObservatory conducted on an on-sky commissioning campaign using the LSST Camera (LSSTCam) to test the end-to-end functionality of hardware and software, as well as operational procedures.
This interim report provides a preliminary technical overview of our understanding of the integrated system performance based tests and analyses conducted during the on-sky commissioning campaign with LSSTCam.
The objectives are to synthesize what we have learned about the system in a timely way to inform Early Operations optimization, and to inform the Rubin science community on the progress of the LSSTCam on-sky campaign.
The report is organized into sections that describe major activities during the campaign, as well as multiple aspects of the demonstrated system and science performance.
All of the results presented here are to be understood as work in progress using engineering data and the initial versions of the data processing pipelines; the report is a living document that will be
updated as analyses are refined.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{YYYY-MM-DD}{Unreleased.}{Bechtol}
}


\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE
% You can also use the \input command to include several content files.

\input{introduction.tex}

\input{summary.tex}

\input{campaign.tex}

\input{calibration_systems.tex}

\input{camera.tex}

\input{throughput.tex}

\input{sky_background.tex}

\input{image_quality.tex}

\input{stray_light.tex}

\input{system_timing.tex}

\input{data_management.tex}

\section{Calibration}
\label{sec:calibration}

\input{psf.tex}

\input{astrometry.tex}

\input{photometry.tex}

\appendix

\section{Acknowledgements}

This material is based upon work supported in part by the National Science Foundation through Cooperative Agreements AST-1258333 and AST-2241526 and Cooperative Support Agreements AST-1202910 and AST-2211468 managed by the Association of Universities for Research in Astronomy (AURA), and the Department of Energy under Contract No.\ DE-AC02-76SF00515 with the SLAC National Accelerator Laboratory managed by Stanford University.
Additional Rubin Observatory funding comes from private donations, grants to universities, and in-kind support from LSST-DA Institutional Members.

% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
%\printglossaries





\end{document}
